---
title: "Using the MATH4753BraydenGarner2025 Package"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Using the MATH4753BraydenGarner2025 Package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

This vignette demonstrates how to use the `MATH4753BraydenGarner2025` package, which contains a variety of functions created by Brayden Garner for MATH4753 for statistical analysis.

```{r}
library(MATH4753BraydenGarner2025)
```

## Example 1: Squaring Numbers

```{r}
# mysq(x) returns x squared
mysq(5) # 25
```

## Example 2: Cubing Numbers

```{r}
# mycubic(x) returns x cubed
mycubic(2) # 8
```

## Example 3: Binomial Simulation

The `mybin()` function simulates a binomial distribution and generates a bar plot of the results. Here, we simulate 10 trials with a success probability of 0.7.

```{r}
mybin(n = 10, p = 0.7)  # Simulates binomial distribution and plots the result
```

## Example 4: Bootstrap Confidence Interval

This example demonstrates the `myboot2()` function, which performs a bootstrap resampling procedure and plots the histogram of the bootstrap sample statistics. A confidence interval is also displayed.

```{r}
# Random sample data for myboot2
set.seed(123)
data <- rnorm(30, mean = 5, sd = 2)

# Bootstrap with 1000 iterations and estimating the mean with a 95% confidence interval
myboot2(iter = 1000, x = data, fun = "mean", alpha = 0.05)
```

# Conclusion

This vignette covered how to use the functions `mysq()`, `mycubic()`, `mybin()`, and `myboot2()` from the `MATH4753BraydenGarner2025` package. These functions provide useful tools for performing basic mathematical operations, probability simulations, and statistical resampling with bootstrapping.
